FITS format for planetary surfaces: definitions, applications and best practices.

### 2018-02-08 ess_marmo.tex
Update on Overleaf.

As an example of non projected planetary data we have converted in FITS format data
acquired by the spectroimager OMEGA on-board of Mars Express.
OMEGA unprojected and uncalibrated data are distributed by ESA-PSA and PDS archives.
Their structure is described in the OMEGA Experiment Archive 
Interface Control Document\footnote{ftp://psa.esac.esa.int/pub/mirror/MARS-EXPRESS/OMEGA/MEX-M-OMEGA-2-EDR-FLIGHT-V1.0/DOCUMENT/EAICD\_OMEGA.PDF}.

@@

\section{Inter-operable software developments}
\label{sec:softdev}
VO-QGIS-plugin\footnote{https://github.com/epn-vespa/VO\_QGIS\_plugin}
MATISSE\footnote{http://tools.asdc.asi.it/matisse.jsp} \citep{ZINZI2016}
Aladin\footnote{http://aladin.u-strasbg.fr/}

>>>>

As an example of non projected planetary data we have converted in FITS format data
acquired by the spectroimager OMEGA on-board of Mars Express.
OMEGA unprojected and uncalibrated data are distributed by ESA-PSA and PDS archives.
Their structure is described in the OMEGA Experiment Archive 
Interface Control Document\footnote{ftp://psa.esac.esa.int/pub/mirror/MARS-EXPRESS/OMEGA/MEX-M-OMEGA-2-EDR-FLIGHT-V1.0/DOCUMENT/EAICD\_OMEGA.PDF}.
\begin{figure}[ht!]
\centerline{\includegraphics[height=17pc]{ess_marmo4}\hspace{60pt}\includegraphics[height=17pc]{ess_marmo3}}
\caption{left: OMEGA data structure (from OMEGA EAICD); right: FITS Multi Digital Object
conversion}
\label{fig:omegascheme}
\end{figure}

TAB projection is implemented in the Calabretta WCSLIB\footnote{http://www.atnf.csiro.au/people/mcalabre/WCS/wcslib/},
available in all major linux distribution, and consequently in all

@@

\section{Inter-operable software developments}
\label{sec:softdev}
VO-QGIS-plugin\footnote{https://github.com/epn-vespa/VO\_QGIS\_plugin}

MATISSE\footnote{http://tools.asdc.asi.it/matisse.jsp} \citep{ZINZI2016}

Aladin\footnote{http://aladin.u-strasbg.fr/}
